---
title: "DiagnosisStudyAnalysis"
date: '2022-11-03'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
    format: readthedown
  pdf_document: default
  word_document: default
  rmdformats::readthedown:
    code_folding: hide
    format: readthedown
    toc_depth: 3
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Set up and aggregation of data

```{r, warning=FALSE, message=FALSE }
## Load Libraries and Python script for processing JSON files##
source("Scripts/packageLoad.R")
source_python("Scripts/processFile.py")
#library(devtools)
#install_github("vqv/ggbiplot")
#library(ggbiplot)
dataFolder <- "../JSONs"
## 1. Load data from JSON files##
## 2. Create full df with stage-wise data##
## 3. Create aggregate dataframe with participant-wise data##
## 4. Create dataframe for case-wise data##
## 5. Create matrix for information seeking data by case##
df <- data.frame(matrix(ncol = 0, nrow = 1584))
infoStages <- c("Geography", "History & Politics", "People & Culture")
accuracyMeasure <- "CorrectLikelihood" #CorrectLikelihood, HighestLikelihood or Accuracy
classifyVar <- "knowledge" #knowledge, accuracy or confidence
ids <- list.dirs(dataFolder,recursive = FALSE) 

countries <-c("KOR","MON","COL","SWI", "GRE", "BOT")
countriesShort <- c("KOR","MON","COL","SWI", "GRE", "BOT")

countriesLong <- c("SOUTH KOREA","MONGOLIA","COLOMBIA","SWITZERLAND", "GREECE","BOTSWANA")

easyCountryGroup <- c("MON", "COL", "KOR") 
hardCountryGroup <- c("SWI", "GRE", "BOT") 

#easyCountryGroup <- c("MON", "KOR") 
#medCountryGroup <- c("SWI", "COL") 
#hardCountryGroup <- c("GRE", "BOT") 

source("Scripts/AggregateData.R")
```


```{r}

count <- 0
accDf <- data.frame(matrix(ncol = 0, nrow = nrow(df)))
for (participantID in participantIDS)
{
  files <- list.files(paste(dataFolder, "/", participantID, sep="")) 
  file <- files[1]
  filePath <- paste(dataFolder, "/", participantID, "/", file, sep="")
  processFile(filePath)
  # Give the input file name to the function.
  myData <- fromJSON(file=filePath)
  trials <- myData$processedData$trials
  for (x in 1:length(trials))
  {
    row <- x + count
    trialSelect <- trials[x]
    trialSelect <- trialSelect[[1]]
    accDf$participantID[row] <- participantID
    accDf$trialNum[row] <- trialSelect$trial
    accDf$stage[row] <- trialSelect$subtrial
    accDf$stageName[row] <- infoStages[trialSelect$subtrial]
    accDf$trueCountry[row] <- toupper(trialSelect$trueCountry)
    
    accDf$differentials[row] <- toString(trialSelect$differentials) 
    accDf$likelihoods[row] <- toString(trialSelect$likelihoods) 
    
    accDf$highestLikelihoodValue[row] <- max(trialSelect$likelihoods)
    differentials <-  accDf$differentials[row]
    differentials <- str_split(differentials,", ")
    differentials <- differentials[[1]]
    accDf$highestLikelihoodDifferential[row] <- differentials[which.max(trialSelect$likelihoods)]
  }
  count <- count + length(trials)
}

```

```{r, echo=FALSE}

# Colour coding for figures
confidenceColour <- "#03c200"
difficultyColour <- "#bf00c2"
infoSeekingColour <- "#ca0600"
differentialColour <- "skyblue"
likelihoodColour <- "orange"
accuracyColour <- "black"
resolutionColour <- "yellow"
```

# Key dependent variables by stage 

```{r, echo=FALSE}

source("Scripts/StagewiseFigures.R")

```

# Key dependent variables by case

```{r, echo=FALSE}

source("Scripts/CountryWiseVariableFigure.R")

```

Information Seeking Analysis:
```{r, echo=FALSE}
#accs <- c("0.3", "0.5", "0.7", "0.8")
#accs <- c("likGroup1", "likGroup2", "likGroup3", "likGroup4")
accs <- c("geoKnowledgeGroup1", "geoKnowledgeGroup2", "geoKnowledgeGroup3", "geoKnowledgeGroup4")
countries <-c("MON", "SWI", "KOR", "COL", "GRE", "BOT")

varBoot <- function(d, i){
	d2 <- d[i,]
	return(sd(d2)^2)
}

numOfClusters <- 4 # 2: initial correctness, 3: case difficulty, 4: ppt accuracy, 6: case
clusterType <- "pam"

source("Scripts/InfoSeekingMDS.R")

```

Correlation Figures:

```{r, echo=FALSE}

source("Scripts/CorrelationFigures.R")

```

# Distributions of Likelihood and Severity Ratings:

```{r, echo=FALSE}

source("Scripts/LikelihoodDists.R")

```

# Classification of performance based on information seeking

```{r, echo=FALSE}

source("Scripts/BinaryClassification.R")

```

# Mixed Effects Modelling: Confidence and Information Seeking

```{r, echo=FALSE}
mixedConModel = lmer(confidenceChange ~ caseInformationProportion + (1 | country) + (1 | id), data = countryDf, na.action="na.exclude")
summary(mixedConModel)

# Assumption testing  
# Linearity
confidenceChange <- countryDf$confidenceChange
modelLin<-plot(residuals(mixedConModel),confidenceChange)

# Homogeneity of variance
countryDf$res<- residuals(mixedConModel) #extracts the residuals 
countryDf$res <-abs(countryDf$res) #absolute value of the residuals
countryDf$res <- countryDf$res^2 #squares the absolute values of the residuals to provide the more robust estimate
Levene.Model.F <- lm(res ~ id, data=countryDf) #ANOVA of the squared residuals
anova(Levene.Model.F) #displays the results

# Normal distribution of residuals
qqmath(mixedConModel, id=0.05, na.rm=TRUE)


```

# Information Seeking and Likelihood of Correct Country:

```{r, echo=FALSE}
correctCases <- countryDf[countryDf$correct==1,]
mixedLikModel = lmer(as.integer(likelihoodOfCorrectCountry) ~ laterInfoProp + (1 | country) + (1 | id), data = correctCases, na.action="na.exclude")
summary(mixedLikModel)
```

# Change in Confidence against Change in Likelihood:

```{r, echo=FALSE}
mixedLikConModel = lmer(confidenceChange ~ likelihoodChange + (1 | country) + (1 | id), data = correctCases, na.action="na.exclude")
summary(mixedLikConModel)
```

```{r, echo=FALSE}
mixedConModel = lm(averageLikelihoodOfCorrectCountryFinal ~ proportionOfInfo + geoScore, data = aggData)
summary(mixedConModel)
```
