---
title: "DiagnosisStudyAnalysis"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: lumen
  pdf_document: default
date: "2022-11-03"
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Load Packages
```{r, warning=FALSE, message=FALSE}
source("Scripts/packageLoad.R")
source_python("Scripts/processFile.py")
```

## Initialise Dataframe

```{r, warning=FALSE, message=FALSE}
## Load Libraries and Python script for processing JSON files##
dataFolder <- "../JSONs"
## 1. Load data from JSON files##
## 2. Create full df with stage-wise data##
## 3. Create aggregate dataframe with participant-wise data##
## 4. Create dataframe for case-wise data##
## 5. Create matrix for information seeking data by case##
df <- data.frame(matrix(ncol = 0, nrow = 1656))
infoStages <- c("Patient History", "Physical Exmination", "Testing")
ids <- list.dirs(dataFolder,recursive = FALSE) 
experiencedIDs <- c("qj4vcw","sz5k4r","kqzd96","s8c6kp","j1bwlt", "jhym2l","gzsfhp")

cases <-c("UC", "GBS", "TA", "TTP", "AD", "MTB")
conditionsShort <- c("UC", "GBS", "TA", "TTP", "AD", "MTB")
conditionsLong <- c("ULCERATIVE COLITIS", "GUILLAINBARRE SYNDROME", "TEMPORAL ARTERITIS", "THROMBOTIC THROMBOCYTOPENIC PURPURA", "AORTIC DISSECTION", "MILIARY TB")

easyCaseGroup <- c("GBS", "UC", "TA") 
hardCaseGroup <- c("AD", "TTP", "MTB") 


easyCaseGroupLong <- c("GUILLAINBARRE SYNDROME", "ULCERATIVE COLITIS", "TEMPORAL ARTERITIS")
hardCaseGroupLong <- c("THROMBOTIC THROMBOCYTOPENIC PURPURA", "AORTIC DISSECTION", "MILIARY TB") 

accuracyMeasure <- "CorrectLikelihood" #HighestLikelihood, CorrectLikelihood, Differential
classifyVar <- "accuracy" #accuracy or confidence
runExclusions <- TRUE

source("Scripts/AggregateData.R")
```

The below code is used to generate a table of differentials to be 'marked' for correctness:

```{r, eval=FALSE}
count <- 0
wd <- dirname(rstudioapi::getSourceEditorContext()$path)
accDf <- data.frame(matrix(ncol = 0, nrow = nrow(df)))
for (participantID in participantIDS)
{
  files <- list.files(paste(wd, "/../JSONs/", participantID, sep="")) 
  file <- files[1]
  filePath <- paste(wd, "/../JSONs/", participantID, "/", file, sep="")
  processFile(filePath)
  # Give the input file name to the function.
  myData <- fromJSON(file=filePath)
  trials <- myData$processedData$trials
  
  for (x in 1:length(trials))
  {
    row <- x + count
    trialSelect <- trials[x]
    trialSelect <- trialSelect[[1]]
    accDf$participantID[row] <- participantID
    accDf$trialNum[row] <- trialSelect$trial
    accDf$stage[row] <- trialSelect$subtrial
    accDf$stageName[row] <- infoStages[trialSelect$subtrial]
    accDf$trueCondition[row] <- toupper(trialSelect$trueCondition)
    
    if (length(trialSelect$diagnoses) > 0)
    {
      accDf$differentials[row] <- toString(trialSelect$diagnoses) 
    }
    else
    {
      accDf$differentials[row] <- toString(trialSelect$differentials) 
    }
    
    liks <- trialSelect$likelihoods
    
    accDf$highestLikelihoodValue[row] <- max(liks)
    differentials <-  accDf$differentials[row]
    differentials <- str_split(differentials,", ")
    differentials <- differentials[[1]]
    
    maxLik <- max(liks)
    numOfMaxDiffs <- sum(liks==maxLik)
    
    if (numOfMaxDiffs == 1)
    {
      accDf$highestLikelihoodDifferential[row] <- differentials[which.max(trialSelect$likelihoods)]
    }
    else
    {
      accDf$highestLikelihoodDifferential[row] <- toString(paste((differentials[which(liks == maxLik)]),sep=""))
    }
    
  }
  count <- count + length(trials)
}



```


```{r, echo=FALSE}

# Colour coding for figures
confidenceColour <- "#03c200"
difficultyColour <- "#bf00c2"
infoSeekingColour <- "#ca0600"
differentialColour <- "skyblue"
likelihoodColour <- "orange"
accuracyColour <- "black"
resolutionColour <- "yellow"
```

## Stagewise Figures

Key dependent variables by stage: 

```{r, echo=FALSE}

source("Scripts/StagewiseFigures.R")

```
## Casewise Figure for DVs

Key dependent variables by case: 

```{r, echo=FALSE}

source("Scripts/CaseWiseVariableFigure.R")

```

## Correlation Figures

```{r, echo=FALSE}

source("Scripts/CorrelationFigures.R")

```

## Distributions of Likelihood and Severity Ratings

```{r, echo=FALSE}

source("Scripts/SeverityAndLikelihoodDists.R")

```

## Information Seeking Analysis
```{r, echo=FALSE, warning=FALSE}
accs <- c("accGroup1", "accGroup2", "accGroup3", "accGroup4", "e")
#if (classifyVar == "confidence")
#{
#  accs <- c("confGroup1", "confGroup2", "confGroup3", "confGroup4")
#} else {
#  accs <- c("accGroup1", "accGroup2", "accGroup3", "accGroup4")
#}
cases <-c("UC", "GBS", "TA", "TTP", "AD", "MTB")
ppts <- c("p", "e")

numOfClusters <- 4# 2: initial correctness, 3: case difficulty, 4: ppt accuracy, 6: case
clusterType <- "pam"
distanceMethod <- "Jaccard" # OPTIONS: Jaccard, cosine, Dice, Euclidean, Hamman

source("Scripts/InfoSeekingMDS.R")

######################################

cor <- cor.test(infoSeekingDf$MDSDistanceVariance,infoSeekingDf$RelativeRationalism,method="pearson")

diffCon <- ggplot(data = infoSeekingDf, aes(x=RelativeRationalism, y=MDSDistanceVariance)) +
  geom_point() +
  geom_smooth(method=lm , color=infoSeekingColour, fill="#69b3a2", se=TRUE) +
  theme_classic()

title <- paste("MSD Distance Variance against Relative Rationalism: ",
               "r(", cor$parameter, ") = ",  round(cor$estimate, 2), ", p = ",  round(cor$p.value,2), sep="")

print(diffCon + 
        ggtitle(title)
      + labs(y="MSD Distance Variance", x = "Relative Rationalism")
      +theme(axis.text=element_text(size=16),
             axis.title=element_text(size=16),
             plot.title=element_text(size=18)
      ))

```

## Classification of Performance by Information Seeking

```{r, echo=FALSE, warning=FALSE}

source("Scripts/BinaryClassification.R")

```

## Modelling

Confidence and Information Seeking:

```{r, echo=FALSE}
mixedConModel = lmerTest::lmer(confidenceChange ~  caseInformationProportion + initialDifferentials + subjectiveDifficulty + likelihoodsUpdated + (1 | caseCode) + (1 | id), REML = TRUE, data = studentCaseDf, na.action="na.exclude")
summary(mixedConModel)


plot(mixedConModel)

# Assumption testing  
# Linearity
confidenceChange <- studentCaseDf$confidenceChange
modelLin<-plot(residuals(mixedConModel),confidenceChange)

# Homogeneity of variance
studentCaseDf$res<- residuals(mixedConModel) #extracts the residuals 
studentCaseDf$res <-abs(studentCaseDf$res) #absolute value of the residuals
studentCaseDf$res <- studentCaseDf$res^2 #squares the absolute values of the residuals to provide the more robust estimate
Levene.Model.F <- lm(res ~ id, data=studentCaseDf) #ANOVA of the squared residuals
anova(Levene.Model.F) #displays the results

# Normal distribution of residuals
qqmath(mixedConModel, id=0.05, na.rm=TRUE)


```

Information Seeking and Likelihood of Correct Diagnosis:

```{r, echo=FALSE}
correctCases <- studentCaseDf[studentCaseDf$correct==1,]
mixedLikModel = lmer(as.integer(likelihoodOfCorrectDiagnosis) ~ laterInfoProp + (1 | condition) + (1 | id), data = correctCases, na.action="na.exclude")
summary(mixedLikModel)
```

Change in Confidence against Change in Likelihood:

```{r, echo=FALSE}
mixedLikConModel = lmer(confidenceChange ~ likelihoodChange + (1 | condition) + (1 | id), data = correctCases, na.action="na.exclude")
summary(mixedLikConModel)
```

Accuracy (as likelihood) against Change in Confidence and Information Seeking:

```{r, echo=FALSE}
mixedInfoConModel = lmer(as.integer(likelihoodOfCorrectDiagnosis) ~ finalConfidence + caseInformationProportion + (1 | condition) + (1 | id), data = correctCases, na.action="na.exclude")
summary(mixedInfoConModel)
```

Relative Rationalism Against Information Seeking

```{r, echo=FALSE}
rationalInfoModel = lm(proportionOfInfo ~ relativeRationalism, data = aggData, na.action="na.exclude")
summary(rationalInfoModel)
```

```{r, echo=FALSE}
mixedCalModel = lmer(brierConfidence ~ caseInformationProportion + initialDifferentials + (1 | condition) + (1 | id), data = studentCaseDf, na.action="na.exclude")
summary(mixedCalModel)
```

Power analysis to determine sample size for a linear model

```{r, echo=FALSE}
pwr.f2.test(u = 1, f2 = 0.15, sig.level = .05, power = .90)
# Cohen suggests f2 values of 0.02, 0.15, and 0.35 represent small, medium, and large effect sizes.
```

Word Cloud of Qualitative Responses on Diagnostic Approaches

```{r, echo=FALSE}

words <- aggData$diagnosticApproach

stopwords_regex = paste(stopwords('en'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
words = stringr::str_replace_all(words, stopwords_regex, '')

dtm <- TermDocumentMatrix(words) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
worddf <- data.frame(word = names(words),freq=words)

set.seed(1234) # for reproducibility 
wordcloud(words = worddf$word, freq = worddf$freq, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))

```


